VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-19 snapshot_system/paper_background.tex
re

Our previous work on parallel deduplication~\cite{zhangusenix13,WeiZhangIEEE} 
is not a comprehensive VM-centric solution and does not address  snapshot deletion and file system block 
packaging for fault tolerance.  The work in ~\cite{zhangusenix13} a low-cost
solution, but requires all backups for each day to occur at the same time and is less flexible than the approach presented here.

>>>>

Our previous work on parallel deduplication~\cite{zhangusenix13,WeiZhangIEEE} 
is not a comprehensive VM-centric solution and does not address  snapshot deletion and file system block 
packaging for fault tolerance.  The work in ~\cite{zhangusenix13} is a low-cost
solution, but requires all backups for each day to occur at the same time and is less flexible than the approach presented here.
